SAT Competition 2020\tnoteref{title}

### 2020-12-17 paper/main.tex
CMU

\address[kit] {
KIT Department of Informatics\\
\url{markus.iser@kit.edu}\\[1em]
}

\address[ctu] {
Czech Technical University in Prague, Czech Republic\\
\url{martin.suda@cvut.cz}\\[1em]
}

>>>>

\address[cmu] {
Computer Science Department, Carnegie Mellon University\\
{\tt marijn@cmu.edu}\\[1em]
}

\address[kit] {
KIT Department of Informatics\\
{\tt markus.iser@kit.edu}\\[1em]
}

\address[ctu] {
Czech Technical University in Prague, Czech Republic\\
{\tt martin.suda@cvut.cz}\\[1em]
}
